DATA 621 - Business Analytics and Data Mining

### 2020-09-24 HW2/HW2-Group2.rmd
Finished through 8

### F1 Score of the Predictions

Function `f1_score` that takes the data set as a dataframe, with actual and predicted classifications identified, and returns the F1 score of the predictions. The formula is:

\[\text{F1 Score} = \frac{2 \times Precision \times Sensitivity}{Precision + Sensitivity}\]

```{r f1_score, echo = TRUE}
f1_score = function(df) {
  if (is.data.frame(df) == FALSE) {
    return("Data set is not a dataframe. Try as.data.frame(dataset).")
  } else {
    return((2 * PRC(df) * SNS(df)) / (PRC(df) + SNS(df)))
  }
}
```

```{r f1_score_check}
sprintf("The F1 score of the predictions for the classification data set is %0.3f.", 
f1_score(class_data))
```

>>>>

# 8. \(F_1\) Score
The function `F1` below takes as input a data frame whose first two columns
are the true class and the modeled class respectively. It returns the
\(F_1\) score of the predictions using the following formula:

\[
\textrm{F}_1\;\textrm{Score} = \frac{2 \times \textrm{Precision} \times
\textrm{Sensitivity}}{\textrm{Precision} + \textrm{Sensitivity}}
\]

```{r f1}
F1 <- function(df) {
  if (!is.data.frame(df)) {
    stop("Data set is not a dataframe. Try as.data.frame(dataset).")
  } else {
    (2 * PRC(df) * SNS(df)) / (PRC(df) + SNS(df))
  }
}
```

For this dataset the \(F_1\) score is
`r prettyNum(F1(class_data) * 100, digits = 5L)`%.
